Fluent statistical computing interfaces for biological data analysis

### 2020-02-21 Rmd/03-fluentGenomics.Rmd
don't cache by default, rebuild output

```{r linkedtxome-ex, eval = FALSE, echo = TRUE}
makeLinkedTxome(
  indexDir=file.path(dir, "gencode.v29_salmon_0.12.0"),
  source="Gencode",
  organism="Homo sapiens",
  release="29",
  genome="GRCh38",
  fasta="ftp://ftp.ebi.ac.uk/pub/databases/gencode/Gencode_human/release_29/gencode.v29.transcripts.fa.gz",
  gtf=file.path(dir, "gencode.v29.annotation.gtf.gz"), # local version
  write=FALSE
)
```

@@

```{r mat-atac, eval=FALSE, echo = TRUE}
atac_mat <- read_tsv("ATAC_cqn_matrix.txt.gz",
                     skip = 1,
                     col_names =c("rownames", atac_coldata[["sample_id"]]))
rownames <- atac_mat[["rownames"]]
atac_mat <- as.matrix(atac_mat[,-1])
rownames(atac_mat) <- rownames
```

@@

```{r atac-se, eval=FALSE, echo = TRUE}
atac <- SummarizedExperiment(assays = list(cqndata=atac_mat),
                             rowRanges=peaks_gr,
                             colData=atac_coldata)
```

>>>>

```{r linkedtxome-ex, eval = FALSE, echo = TRUE}
makeLinkedTxome(
  indexDir=file.path(dir, "gencode.v29_salmon_0.12.0"),
  source="Gencode",
  organism="Homo sapiens",
  release="29",
  genome="GRCh38",
  fasta="gencode.v29.transcripts.fa.gz", # ftp link to fasta file
  gtf=file.path(dir, "gencode.v29.annotation.gtf.gz"), # local version
  write=FALSE
)
```

@@

```{r mat-atac, eval=FALSE, echo = TRUE}
atac_mat <- read_tsv(
  "ATAC_cqn_matrix.txt.gz",
  skip = 1,
  col_names = c("rownames", atac_coldata[["sample_id"]])
 )
rownames <- atac_mat[["rownames"]]
atac_mat <- as.matrix(atac_mat[,-1])
rownames(atac_mat) <- rownames
```

@@

```{r atac-se, eval=FALSE, echo = TRUE}
atac <- SummarizedExperiment(
  assays = list(cqndata=atac_mat),
  rowRanges = peaks_gr,
  colData = atac_coldata
)
```

### 2020-02-21 index.Rmd
don't cache by default, rebuild output

opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE,
  fig.path = here::here('img/'), fig.align = 'center', fig.show = 'hold',
  cache = TRUE, external = TRUE, comment = "#>", dpi = 300,
  out.width = ifelse(is_html_output(), "100%", "\\textwidth"),
  cache.path = ifelse(is_html_output(), 
                      here::here('cache-gitbook/'), 
                      here::here('cache-pdfbook/')
  )
)

>>>>

opts_chunk$set(
  warning = FALSE, message = FALSE, echo = FALSE,
  fig.path = here::here('img/'), fig.align = 'center', fig.show = 'hold',
  external = TRUE, comment = "#>", dpi = 300,
  out.width = ifelse(is_html_output(), "100%", "\\textwidth"),
  cache.path = ifelse(is_html_output(), 
                      here::here('cache-gitbook/'), 
                      here::here('cache-pdfbook/')
  )
)
